---
title: '614'
author: "Jingyi Ge"
date: "1/22/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.find the square root of 169
```{r}
sqrt(169)
```
2.raise 12 to the second power
```{r}
12^2
12**2
```

3.raise 1/8 to the third power.
```{r}
(1/8)^3
```

4.evalute 6 times the difference between the square of 5 and 3
```{r}
6*(5^2-3)
```

5.
```{r}
log10(100)
```

6. write all integers 1 to 25 inclusive in ascending/descending order.
```{r}
1:25
25:1
```

8.find the sum /mean/ median of all integers 1 to 25
```{r}
sum(1:25)
mean(1:25)
median(1:25)
summary(1:25)
```

12.
```{r}
sample(x=1:6,size=1)
```

13.round 7.2557 to the nearest tenth.
```{r}
round(7.2557,1)
```

14.find the cube root of 216
```{r}
(216)^(1/3)
```

15. round the following numbers to the nearest hundredth.
   16.1766, 8.512, 70.104, 200.437, 10001.0884
```{r}
x <- c(16.1766, 8.512, 70.104, 200.437, 10001.0884)
round(x,2)
```

16.find the numerical approximation for e.
```{r}
exp(1)
```

17.
```{r}
log(17)
```

18.find the numerical approximation for pie
```{r}
round(pi,1)
pi
```

```{r}
library(tidyverse)
library(ggplot2)
view(mpg)
```

```{r}
boxplot(mpg$hwy)
```

```{r}
ggplot(mpg,aes(x=drv,y=cty)) +
  geom_boxplot()
```

```{r}
hist(mpg$cty)
```

```{r}
stem(mpg$cty)
```

q()
y

